---
title: "Vignettes"
author: "Julia_Vassey"
date: "5/3/2019"
output: html_document
vignette: >
  %\VignetteIndexEntry{Binomial}
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
  
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


## Binomial

The package `"binomial"` allows a user to build a binomial distribution data frame and plot a distribution. To implement this task, the package contains a number of functions from choosing number of successes in trials, to distribtion probabilities to making auxilary functions, incuding mean, median and mode. 


## Creating 'bin_choose'  

The first step is to create a `"bin_choose" function that returns us the number of ways we can choose success out of the total number of trials.

```{r}
bin_choose <- bin_choose(n=5, k=4)
bin_choose
```


## Creating 'bin_probability' 

The function returns the probability of successes out of the total number of trials.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability()

```

## Creating 'bin_distribution' 

The function returns probability in binomial distribution in a dataframe with two columns: success and probability.

```{r}
bin_distribution(trials = 5, prob = 0.5)
```


## Crearting "plot.bindis"

The function returns the plot distribution of successes

```{r}
plot.bindis(trials = 5, prob = 0.5)

```

## Creating 'bin_cumulative' function

The function returns us cumulative probability and a dataframe with three columns: success, probability and 
cumulative.
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```


## Creating 'bin_variable' function

The function returns us a list of porbabilites and success followed by print.binvar function that prints the numer of trials and the probability of success. 

```{r, fig.show='hold'}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

## Creating auxilary functions for mean, vairnce, mode, kurtosis and skewness in the binomial distribution.

```{r cars}
aux_mean(7,0.2)
aux_variance(7,0.7)
aux_mode(7,0.5)
aux_kurtosis(7,0.5)
aux_skewness(7,0.9)
```

## Creating summary.binvar function

The function returns the number of trials and probability with mean, variance, mode, skewness and kurtosis and prints the values with summary.binvar

```{r pressure, echo=FALSE}
x1 <- bin_variable(10, 0.5)
summary.binvar(x1)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
